Novelty Detection for Semantic Place Categorization

### 2011-07-14 thesis/presentation.tex
More changes in thesis presentation

\subsection{Mapping}
\begin{frame}{Mapping - Machine Friendly}
\begin{columns}[c]
\column{0.5\textwidth}
  \begin{figure}
    \includegraphics[width=\textwidth]{figures/machinefriendly.jpg}
  \end{figure}

@@

  \only<2>{
  \begin{figure}
  \begin{tikzpicture}
    % \draw [help lines] grid(3,2);

@@

  \end{tikzpicture}
  \end{figure}
  }
\end{columns}
\end{frame}

\subsection{Semantic Mapping}
\begin{frame}{Semantic Mapping}
\begin{columns}[c]

\column{0.5\textwidth}
  \begin{figure}
    \includegraphics[width=\textwidth]{figures/semanticfriendly.jpg}
  \end{figure}

@@

    \node[ellipse callout, draw, callout absolute pointer={(robot.north)},
          text width=0.2\textwidth]
          (robotvoice) at (3,2) {In the kitchen};

@@

\begin{block}{Dynamic Sample-Space}
As more information becomes available, the .

The question is on how to define a threshold under this circumstances. 
\end{block}
\end{frame}

\subsection{Conditional and Unconditional Ratio}
\begin{frame}{Ordering the Sample Space}

\begin{block}{Back to the Roots}
An optimal detector can be implemented by defining a threshold over a
relation order defined by $P(\overline{novel}|x)$.
\end{block}
\vfill

@@

\begin{frame}{Unconditional Probability Model}
\only<1>{
\begin{columns}[c]
  \column{0.5\textwidth}
  \input{uniform-distribution.tikz}
  \column{0.5\textwidth}
  \input{bigfactor-distribution.tikz}
\end{columns}
}
\only<2>{
\begin{columns}[c]
 \column{0.5\textwidth}
  \input{uniformfac-distribution.tikz}

@@

@@

\section{Conclusion}

\subsection{Summary}
\begin{frame}{Summary}
\begin{itemize}
\item Studies a semantic mapping process
\item Studies novelty detection
\item Proposes a method to perform detection of novel categories
      of a variable type of a graphical model when the graph structure
      is dynamic.
\end{itemize}
\end{frame}

>>>>

\subsection{Mapping}
\begin{frame}{Mapping - Machine Friendly}
\begin{columns}[tc]
\column{0.5\textwidth}
  \begin{figure}
    \only<1>{\includegraphics[width=\textwidth]{figures/extra/pointcloud.jpg}}
    \only<2>{\includegraphics[width=\textwidth]{figures/machinefriendly.pdf}}
  \end{figure}

@@

  \only<2>{
  \begin{tikzpicture}
    % \draw [help lines] grid(3,2);

@@

  \end{tikzpicture}
  }
\end{columns}
\end{frame}

\subsection{Semantic Mapping}
\begin{frame}{Semantic Mapping}
\begin{columns}[tt]

\column{0.5\textwidth}
  \begin{figure}
    \includegraphics[width=\textwidth]{figures/semanticfriendly.pdf}
  \end{figure}

@@

    \node[ellipse callout, draw, callout absolute pointer={(robot.north)},
          text width=0.2\textwidth]
          (robotvoice) at (3,2) {In the office};

@@

\begin{block}{Dynamic Sample Space}
As more information becomes available the probability mass spreads around and
the threshold for novelty detection needs to be adjusted.
\alert<2->{How to do it?}
\end{block}
\end{frame}

\subsection{Conditional and Unconditional Ratio}
\begin{frame}{Ordering the Sample Space}
\begin{block}{Back to the Roots}
An optimal detector can be implemented by defining a threshold over a
relation order defined by $P(\overline{novel}|x)$.
\end{block}
\vfill

@@

\begin{frame}{Unconditional Probability Model}
\only<1>{
\begin{columns}[t]
  \column{0.5\textwidth}
  \input{uniform-distribution.tikz}

  \centering
  No prior knowledge on $P(x)$. \\
  Uniform distribution~\cite{shore1980axiomatic}

\column{0.5\textwidth}
  \input{bigfactor-distribution.tikz}

  \centering
  Assume structure and knowledge on other variables still hold true on $P(x)$
\end{columns}
}
\only<2>{
\begin{columns}[c]
 \column{0.5\textwidth}
  \input{uniformfac-distribution.tikz}

@@

\begin{columns}[c]
\column{0.5\textwidth}
\begin{tikzpicture}
  \node [matrix,matrix anchor=mid, column sep=10pt, row sep=10pt,ampersand replacement=\&] {
    \& \& \node (room) [latent] {$r$}; \& \& \\
    \& \& \& \& \\
    \node (f1) [factor] {}; \&
    \node (f2) [factor] {}; \&
    \node (f3) [factor] {}; \&
    \node (fi) [] {\dots}; \&
    \node (fn) [factor] {}; \\
    \node (x1) [obs] {$x_1$}; \&
    \node (x2) [obs] {$x_2$}; \&
    \node (x3) [obs] {$x_3$}; \&
    \node (xi) [] {\dots}; \&
    \node (xn) [obs] {$x_n$}; \\
  };
  \draw [-] (room) -- (f1) -- (x1);
  \draw [-] (room) -- (f2) -- (x2);
  \draw [-] (room) -- (f3) -- (x3);
  \draw [-] (room) -- (fi);
  \draw [-] (room) -- (fn) -- (xn);

  \node (captf1) [right=2pt of f1] {\footnotesize{$\phi_{X_1}$}};
  \node (captf2) [right=2pt of f2] {\footnotesize{$\phi_{X_2}$}};
  \node (captf3) [right=2pt of f3] {\footnotesize{$\phi_{X_3}$}};
  \node (captfn) [right=2pt of fn] {\footnotesize{$\phi_{X_n}$}};
\end{tikzpicture}
\column{0.5\textwidth}

\begin{block}{Room class generator of features}
\begin{itemize}
  \item 11 - Room Categories
  \item 2 - Room Shapes (laser)
  \item 3 - Room Size (laser)
  \item 10 - Room Appearance (CRFH)
  \item 7 - Object Detectors (SIFT)
\end{itemize}
\end{block}
\end{columns}
\end{frame}

\begin{frame}{Synthetic Dataset - Conditional Model}
\begin{block}{Conditional Model}
\centering
\begin{tikzpicture}
  \node [matrix,matrix anchor=mid, column sep=10pt, row sep=10pt,ampersand replacement=\&] {
    \& \& \node (room) [latent] {$r$}; \& \& \\
    \& \& \& \& \\
    \node (f1) [factor] {}; \&
    \node (f2) [factor] {}; \&
    \node (f3) [factor] {}; \&
    \node (fi) [] {\dots}; \&
    \node (fn) [factor] {}; \\
    \node (x1) [obs] {$x_1$}; \&
    \node (x2) [obs] {$x_2$}; \&
    \node (x3) [obs] {$x_3$}; \&
    \node (xi) [] {\dots}; \&
    \node (xn) [obs] {$x_n$}; \\
  };
  \draw [-] (room) -- (f1) -- (x1);
  \draw [-] (room) -- (f2) -- (x2);
  \draw [-] (room) -- (f3) -- (x3);
  \draw [-] (room) -- (fi);
  \draw [-] (room) -- (fn) -- (xn);

  \node (captf1) [right=2pt of f1] {\footnotesize{$\phi_{X_1}$}};
  \node (captf2) [right=2pt of f2] {\footnotesize{$\phi_{X_2}$}};
  \node (captf3) [right=2pt of f3] {\footnotesize{$\phi_{X_3}$}};
  \node (captfn) [right=2pt of fn] {\footnotesize{$\phi_{X_n}$}};
\end{tikzpicture}

Trained from data sampled from 5 of the 11 room categories.
\end{block}
\end{frame}

\begin{frame}{Synthetic Dataset - Unconditional Models}

\begin{block}{Uniform Model}
\centering
\begin{tikzpicture}
  \node [matrix,matrix anchor=mid, column sep=10pt, row sep=10pt,ampersand replacement=\&] {
    \node (x1) [obs] {$x_1$}; \&
    \node (x2) [obs] {$x_2$}; \&
    \node (x3) [obs] {$x_3$}; \&
    \node (xi) [] {\dots}; \&
    \node (xn) [obs] {$x_n$}; \\
  };
\end{tikzpicture}
\end{block}

\begin{block}{Independent Model}
\centering
\begin{tikzpicture}
  \node [matrix,matrix anchor=mid, column sep=20pt, row sep=10pt,ampersand replacement=\&] {
    \& \& \& \& \\
    \node (f1) [factor] {}; \&
    \node (f2) [factor] {}; \&
    \node (f3) [factor] {}; \&
    \node (fi) [] {\dots}; \&
    \node (fn) [factor] {}; \\
    \node (x1) [obs] {$x_1$}; \&
    \node (x2) [obs] {$x_2$}; \&
    \node (x3) [obs] {$x_3$}; \&
    \node (xi) [] {\dots}; \&
    \node (xn) [obs] {$x_n$}; \\
  };
  \draw [-] (f1) -- (x1);
  \draw [-] (f2) -- (x2);
  \draw [-] (f3) -- (x3);
  \draw [-] (fi);
  \draw [-] (fn) -- (xn);
\end{tikzpicture}

Factors were trained using samples drawn from the synthetic distribution where the label
for the generating class was hidden.
\end{block}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}

\subsection{Summary}
\begin{frame}{Summary}
\begin{itemize}
\item Studies a semantic mapping process
\item Studies novelty detection
\item Proposes a method to perform detection of novel categories
      of a variable when the graph structure is dynamic.
\end{itemize}
\end{frame}
